---
title: "Coffe Rating \n tidytuesday #28"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
library(tidyverse);
library(tidymodels);
library(tidymetrics);
library(skimr);
library(tidytext);
library(AnomalyDetection);
library(corrplot);
library(ggrepel);
library(broom);
library(lubridate);
theme_set(theme_light())
```


## Explorartory Data Analysis 


```{r, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
tuesdata <- tidytuesdayR::tt_load(2020, week = 28)
coffee_ratings <- tuesdata$coffee_ratings
coffee_ratings%>%
  head()
```



```{r}
coffee_ratings%>%
  count(species,sort = TRUE)

coffee_ratings%>%
  count(country_of_origin,sort = TRUE)
```



```{r}
coffee_ratings%>%
  filter(!is.na(country_of_origin))%>%
  group_by(country_of_origin,species)%>%
  summarize(total=n())%>%
  arrange(desc(total))%>%
  ungroup()%>%
  ggplot(aes(fct_reorder(country_of_origin,total),total,fill=species))+
  geom_col(show.legend = TRUE)+
  coord_flip()+
  labs(x='',
       y='Total',
       title = 'Relation Between Contry and Coffe-Type',
       caption = '#Undatascientistdice')
```


```{r}
coffee_ratings%>%
  filter(!is.na(country_of_origin))%>%
  group_by(country_of_origin)%>%
  summarize(avg_points=mean(total_cup_points))%>%
  arrange(desc(avg_points))%>%
  mutate(country_of_origin=fct_reorder(country_of_origin,avg_points))%>%
  ggplot(aes(avg_points,country_of_origin,color=avg_points>mean(coffee_ratings$total_cup_points)))+
  geom_errorbarh(aes(xmin=mean(coffee_ratings$total_cup_points),xmax=avg_points),height = 0)+
  geom_vline(xintercept = mean(coffee_ratings$total_cup_points),linetype='dashed')+
  geom_point()+
  labs(y='',
       x='Avegare Rating',
       title = 'Average Rating Coffe per Contry',
       caption = '#Undatascientistdice')+
  guides(color=FALSE,
         size=FALSE)+
  theme(plot.title = element_text(hjust = 0.5))
```



```{r}
coffee_ratings%>%
  filter(!is.na(country_of_origin))%>%
  ggplot(aes(fct_reorder(country_of_origin,total_cup_points),total_cup_points,fill=country_of_origin))+
  geom_boxplot(outlier.colour = 'red')+
  coord_flip()+
  labs(x='country',
       y='Rating Scale Ratio')+
  guides(fill=FALSE)
```

> Is necessary do an anomaly detection analysis


```{r,echo=FALSE, cache=FALSE}
coffe_anom<-AnomalyDetectionVec(coffee_ratings$total_cup_points,max_anoms = 0.4,direction = 'both',period = 12,plot = TRUE)
coffe_anom$plot
```




```{r}
coffee_ratings%>%
  filter(!is.na(country_of_origin))%>%
  filter(!total_cup_points %in% coffe_anom$anoms$anoms)%>%
  mutate(country_of_origin=fct_reorder(country_of_origin,total_cup_points))%>%
  ggplot(aes(total_cup_points,country_of_origin,fill=country_of_origin))+
  geom_boxplot()+
  guides(fill=FALSE)+
  labs(x='Rating without anomalies',
       y='Country',
       title = 'Relation Between Country - Total Cup Points')
```

```{r}
coffee_wa<-coffee_ratings%>%
  filter(!is.na(country_of_origin))%>%
  filter(!total_cup_points %in% coffe_anom$anoms$anoms)
coffee_wa%>%
  ggplot(aes(total_cup_points,fill=species))+
  geom_histogram()+
  facet_wrap(~species,scales = 'free')+
  guides(fill=FALSE)
```

```{r}
coffee_wa%>%
  ggplot(aes(total_cup_points,fill=species))+
  geom_histogram()+
  facet_wrap(~country_of_origin,scales = 'free_y')+
  guides(fill=FALSE)
```



```{r}
coffee_cross<-coffee_wa%>%
  group_by(country_of_origin)%>%
  summarize(across(c(total_cup_points,aroma:moisture), list(
    avg =mean,
    total =sum,
    median =median
  )))

coffee_cross%>%
  arrange(desc(total_cup_points_avg))%>%
  mutate(country_of_origin=fct_reorder(country_of_origin,aroma_total))%>%
  ggplot(aes(aroma_total,country_of_origin,fill=total_cup_points_avg))+
  geom_col()+
  labs(fill='Average Rating',
       y='Country')
```

With this Graph, I Understan that `Aroma` not is a faithfil factor for coffe quality. I love this input!! 
😃

### Explore some correlation 

```{r}
coffee_correlation<-coffee_wa%>%
  select(total_cup_points,where(is.numeric))%>%
  select(-c(category_one_defects,quakers,altitude_low_meters,altitude_high_meters,altitude_mean_meters))%>%
  scale()%>%
  cor()

coffee_correlation
```


```{r,echo=FALSE, cache=FALSE}
coffee_correlation%>%
  corrplot(method = 'circle',type="upper",order="hclust")
```


With this correlation I think that I can develped some Feature Engineer. But First I need Undertad other insights😃


```{r}
coffee_cross%>%
  ggplot(aes(flavor_avg,total_cup_points_avg))+
  geom_jitter(alpha=1/3)+
  geom_text_repel(aes(label=country_of_origin))
```


```{r}
coffee_cross%>%
  ggplot(aes(flavor_total,total_cup_points_avg))+
  geom_jitter(alpha=1/3)+
  geom_text_repel(aes(label=country_of_origin))+
  labs(x='Flavor',
       y='Avg Rating of Preference',
       title = 'Relation Between Rating and Flavor')
```


I think that with `Aroma` can I develop a deeper analysis.



```{r}
coffee_cross%>%
  ggplot(aes(aroma_avg,flavor_avg))+
  geom_point(aes(size=total_cup_points_total,color=country_of_origin))+
  geom_text_repel(aes(label=country_of_origin))+
  labs(size='Total Rating',
       x='Average Aroma',
       y='Average Flavor',
       title = 'Taste structure for coffee',
       caption= '#Undatascientistdice')+
  guides(color=FALSE)
```



This is interesting, a high rate of flavor or aroma it's not decisive to be better cataloged.

```{r}
coffee_cross%>%
  ggplot(aes(aroma_avg,aftertaste_avg))+
  geom_point(aes(size=total_cup_points_total,color=country_of_origin))+
  geom_text_repel(aes(label=country_of_origin))+
  labs(size='Total Rating',
       x='Average Aroma',
       y='Average Aftertaste',
       title = "Taste structure for coffee",
       caption= '#Undatascientistdice')+
  guides(color=FALSE)
```


This is incredible insigths!! `Aftertaste grade` is the most importat for create new levels in the `rating`.



## Feature Engineering



```{r}
coffee_wa$harvest_year<-as.numeric(coffee_wa$harvest_year)
coffee_wa<-coffee_wa%>%
  mutate(harvest_year=gsub("[^0-9.-]+","",harvest_year),
         expiration=lubridate::mdy(expiration))

numerical_features<-coffee_wa%>%
  select(total_cup_points,where(is.numeric))%>%
  select(-c(altitude_low_meters,altitude_high_meters,altitude_mean_meters))%>%
  lm(total_cup_points~ ., data = .)%>%
  tidy()%>%
  filter(p.value<=.05)%>%
  select(term)
categorical_features<-  
coffee_wa%>%
  select(total_cup_points,where(is.character))%>%
  select(-c(lot_number,ico_number,altitude,certification_address,certification_contact,unit_of_measurement))%>%
  lm(total_cup_points~ ., data = .)%>%
  tidy()%>%
  filter(p.value<=.05)%>%
  select(term)%>%
  mutate(new_term=str_replace_all(term,('owner'),''),
         new_term=str_replace_all(new_term,('country_of_origin'),''),
         new_term=str_replace_all(new_term,('farm_name'),''),
         new_term=str_replace_all(new_term,('mill'),''),
         new_term=str_replace_all(new_term,('region'),''),
         new_term=str_replace_all(new_term,('producer'),''),
         new_term=str_replace_all(new_term,('grading_date'),''))%>%
  select(new_term)
  

categorical_features
```


```{r}

model_for_country<-coffee_wa%>%
  select(total_cup_points,country_of_origin,any_of(numerical_features$term))%>%
  group_by(country_of_origin)%>%
  summarize(models=list(lm(total_cup_points~aroma+flavor+aftertaste+acidity+body+balance+uniformity+clean_cup+sweetness+cupper_points)))%>%
  mutate(tidied=map(models,tidy))%>%
  unnest(tidied)%>%
  filter(p.value<=0.05)

coffee_glance<-coffee_wa%>%
  select(total_cup_points,country_of_origin,any_of(numerical_features$term))%>%
  group_by(country_of_origin)%>%
  summarize(models=list(lm(total_cup_points~aroma+flavor+aftertaste+acidity+body+balance+uniformity+clean_cup+sweetness+cupper_points)))%>%
  mutate(glanced=map(models,broom::glance))%>%
  unnest(glanced)%>%
  filter(!is.na(r.squared),
         !is.na(adj.r.squared))

```




```{r}
bad_fit<-coffee_glance%>%
  filter(r.squared<0.25)

coffee_wa%>%
  semi_join(bad_fit,by='country_of_origin')%>%
  ggplot(aes(aroma,total_cup_points,color=factor(country_of_origin)))+
  geom_line(group=1)+
  labs(title = 'Poor Accuracy for Predictions')

```


## Build a model



```{r}
coffee_wa%>%
  anti_join(bad_fit,by='country_of_origin')%>%
  ggplot(aes(aroma,total_cup_points,color=factor(country_of_origin)))+
  geom_line(group=1)+
  labs(title = 'Good Accuracy Levels for predictions',
       subtitle = 'Under Feature')+
  facet_wrap(~country_of_origin)+
  guides(color=FALSE)
```


### Models 

For create this model is necessary understand the residuals behavior .

```{r, warning=FALSE}
coffee_wa%>%
  select(total_cup_points,country_of_origin,any_of(numerical_features$term))%>%
  group_by(country_of_origin)%>%
  summarize(models=list(lm(total_cup_points~aroma+flavor+aftertaste+acidity+body+balance+uniformity+clean_cup+sweetness+cupper_points)))%>%
  mutate(augmented=map(models,broom::augment))%>%
  unnest(augmented)%>%
  ggplot(aes(total_cup_points,.resid,color=country_of_origin))+
  geom_point(alpha=1/3)+
  geom_smooth()+
  facet_wrap(~country_of_origin,scales = 'fixed')+
  guides(color=FALSE)
```

```{r}
bad_counties<-c('Vietnam','Zambia','Rwanda','Papua New Guinea','Japan','Mauritius','Cote d?lvoire')

```

```{r}
data_for_model<-coffee_wa%>%
  filter(!country_of_origin %in% bad_counties)%>%
  group_by(country_of_origin)%>%
  select(total_cup_points,any_of(numerical_features$term))

pca_recipe <- recipe(total_cup_points~., data = data_for_model)
pca_trans <- pca_recipe %>%
  step_center(all_numeric()) %>%
  step_scale(all_numeric()) %>%
  step_pca(all_numeric())

pca_estimates <- prep(pca_trans)
sdev <- pca_estimates$steps[[3]]$res$sdev
percent_variation <- sdev^2 / sum(sdev^2)
var_df <- data.frame(PC=paste0("PC",1:length(sdev)),
                     var_explained=percent_variation,
                     stringsAsFactors = FALSE)
```


```{r}
var_df %>%
  mutate(PC = fct_inorder(PC)) %>%
  ggplot(aes(x=PC,y=var_explained))+geom_col()
```



```{r}
juice(pca_estimates) %>%
  ggplot(aes(PC1, PC2)) +
  geom_point(aes(color = country_of_origin), alpha = 0.7, size = 2)+
  labs(title="PCA from Coffee Models")
```



```{r}
coffee_rec <- recipe(total_cup_points ~ ., data = data_for_model) %>%
  update_role(country_of_origin,new_role = "id")%>%
  step_normalize(all_predictors()) %>%
  step_pca(all_predictors())

coffee_prep <- prep(coffee_rec)

coffee_prep
```


```{r}
tidied_pca <- tidy(coffee_prep, 2)

tidied_pca %>%
  mutate(component = fct_inorder(component)) %>%
  ggplot(aes(value, terms, fill = terms)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~component) +
  labs(y = NULL)
```


```{r}
tidied_pca %>%
  filter(component %in% c("PC1", "PC2", "PC3", "PC4","PC5","PC6")) %>%
  group_by(component) %>%
  top_n(6, abs(value)) %>%
  ungroup() %>%
  mutate(terms = reorder_within(terms, abs(value), component)) %>%
  ggplot(aes(abs(value), terms, fill = value > 0)) +
  geom_col() +
  facet_wrap(~component, scales = "free_y") +
  scale_y_reordered() +
  labs(
    x = "Absolute value of contribution",
    y = NULL, fill = "Positive?"
  )
```

```{r}
juice(coffee_prep) %>%
  filter(!country_of_origin %in% bad_counties)%>%
  count(country_of_origin,sort = TRUE)%>%
  filter(n>10)->filter_data
juice(coffee_prep) %>%
  filter(country_of_origin %in% filter_data$country_of_origin)%>%
  lm(total_cup_points~.,data=.)%>%
  augment()%>%
  mutate(reiduals=total_cup_points-.resid)%>%
  ggplot(aes(total_cup_points,reiduals,color=country_of_origin))+
  geom_point(alpha=1/3)+
  geom_smooth()+
  facet_wrap(~country_of_origin,scales = 'fixed')


```



