---
title: "Ikea models"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,message = FALSE)
```


## Ikea  

```{r}
#Libraries 
library(tidyverse)
library(tidymodels)
library(tidytext)
library(widyr)
library(skimr)
library(glue)
library(scales)
library(ggridges)
library(broom)
library(usemodels)
library(textrecipes)
library(keras)
theme_set(theme_classic())
cap='#Undatascientistdice'
```


```{r}
ikea <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv')%>%
  select(-c(X1,link))
```



## Exploratory Data Analysis

```{r}
ikea%>%
  skim()
```
### Preprocesing

```{r}
ikea <- ikea %>%
   transform(name = as.factor(name),
             category = as.factor(category),
             old_price = as.factor(old_price),
             other_colors = as.factor(other_colors),
             short_description = as.factor(short_description),
             designer = as.factor(designer),
             price= price * 0.27)

ikea%>%
  glimpse()
```


```{r}
ikea%>%
  count(category, sort = TRUE)%>%
  mutate(category = fct_reorder(category,n))%>%
  ggplot(aes(n,
             category,
             fill = category,
             color = category))+
  geom_col(alpha=0.5, 
           show.legend = FALSE)+
  labs(title = 'The most common Ikea`s category',
       x ='# of items',
       y = '',
       caption= cap)+
  theme(plot.title = element_text(hjust = 0.5,face = 'bold'))

```


```{r, fig.height=6}
ikea_category_designer <- ikea%>%
   group_by(category,designer)%>%
   count(sort = TRUE)%>%
   filter(n>=10)

ikea_category_designer%>%
  ungroup()%>%
  filter(category != 'Beds')%>%
  mutate(designer=reorder_within(designer,n,category))%>%
  ggplot(aes(n,
             designer,
             color= category))+
  geom_errorbarh(aes(xmin=0,xmax=n),
                 height=0, 
                 color='grey',
                 show.legend = FALSE,
                 alpha=0.5)+
  geom_point(show.legend = FALSE, aes(size = n))+
  scale_y_reordered()+
  facet_wrap(~category, scales = 'free_y')+
  labs(y = 'Designer',
       x = 'Total of projects',
       title = 'Relation between Ikeas`s Category/Designer',
       caption = cap)
  
```


```{r}
ikea%>%
  ggplot(aes(price, fill = category))+
  geom_histogram(show.legend = FALSE,bins = 10)+
  facet_wrap(~category, scales = 'free_y')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y ='',
       x = 'Price',
       title = 'Distribution Price per Category',
       caption = cap)
```

```{r, fig.height=6}
ikea%>%
  group_by(category,designer)%>%
  summarize(avg_price = mean(price),
            min_price = min(price),
            max_price = max(price))%>%
  ungroup()%>%
  mutate(designer=reorder_within(designer,avg_price,category))%>%
  top_n(18)%>%
  ggplot(aes(avg_price,
             designer,
             color=category))+
  geom_errorbarh(aes(xmin=min_price,xmax=max_price, height = 0), show.legend = FALSE)+
  geom_point(show.legend = FALSE, aes(size= avg_price))+
  scale_y_reordered()+
  facet_wrap(~category, scales = 'free_y')+
  labs(title = 'Relation Price-Designer per Category',
       y = 'Designer',
       x = 'Average Price')
```




```{r}
ikea%>%
  mutate(category = fct_reorder( category, price))%>%
  ggplot(aes(price,
             category))+
  geom_boxplot()+
  geom_jitter(alpha = 0.20, width = 0, height = .1)+
  scale_x_log10()
```

Here we can find the real candidate for outliers price in this dataset, but is necesary agregate the total elements for category.



```{r}
ikea%>%
  add_count(category, name = 'category_total')%>%
  mutate(category = glue("{ category} ({category_total})"),
         category = fct_reorder(category, price))%>%
  ggplot(aes(price,category))+
  geom_boxplot()+
  geom_jitter(alpha = 0.20, width = 0, height = .1)+
  scale_x_log10(labels = dollar)+
  labs(y = '',
       x= 'Price (log Price)',
       title = 'How much do items in each category cost?')
  
```

```{r}
ikea%>%
  add_count(category, name = 'category_total')%>%
  mutate(category = glue("{ category} ({category_total})"),
         category = fct_reorder(category, price))%>%
  ggplot(aes(price,category, fill = other_colors))+
  geom_density_ridges(alpha = 0.5)+
  scale_x_log10(labels = dollar)+
  
  labs(y = '',
       x= 'Price (log Price)',
       title = 'How much do items in each category cost?',
       fill = 'Other Colors')
```

```{r}
ikea%>%
  mutate(name= fct_lump(name,20))%>%
  filter(name!= 'Other')%>%
  count(name,category,sort=TRUE)%>%
  mutate(name = fct_reorder(name,n,sum),
         category = fct_reorder(category,n,sum))%>%
  ggplot(aes(n,
         name,
         fill=category))+
  geom_col()
```


```{r}
ikea%>%
  separate(short_description, c("main_description","rest"),", ", 
           extra = 'merge',
           fill = "right",
           remove = FALSE)%>%
  extract(rest,"numbers","([\\d\\-xX]+) cm", remove = FALSE)%>%
  unite(category_description, category, main_description)%>%
  count(category_description, sort=TRUE)
```




```{r}
ikea_volumes <- ikea%>%
   select(name,category,short_description,price,depth,height,width)%>%
  mutate(volume = depth * height * width /1000000)%>%
  filter(!is.na(volume))%>%
  add_count(category,name = "category_total")


ikea_volumes%>%
  mutate(category = glue("{ category} ({category_total})"),
         category = fct_reorder(category, volume))%>%
  ggplot(aes(volume,category))+
  geom_boxplot()+
  scale_x_log10()+
  labs(x='Volume m^3')


```

```{r}
ikea_volumes%>%
  mutate(category = fct_lump(category,6))%>%
  ggplot(aes(volume,price,  color = category))+
  geom_point()+
  geom_smooth(method = 'lm')+
  scale_x_log10()+
  scale_y_log10()

```

### Choosing variables for the model.




```{r}
ikea%>%
  mutate(volume = depth * height * width /1000000)%>%
  filter(!is.na(volume))%>%
  lm(log2(price)~ log2(volume) + category  ,data = .)%>%
  tidy(conf.int=TRUE)%>%
  filter(term!='(Intercept)')%>%
  mutate(term = str_remove(term,"^category"))%>%
  mutate(term= fct_reorder(term,estimate))%>%
  ggplot(aes(estimate,term))+
  geom_point()+
  geom_errorbarh(aes(xmin = conf.low,xmax=conf.high), height =.1)+
  geom_vline(xintercept = 0, color='red',lty = 2)
```
This relation have double impact, for this i think that the best option is with a machine learning model for eliminate linear trends. But maybe some insights here I can use how to feature.


### Build a models



```{r}
ikea_df <- ikea %>%
   mutate(volume = depth * height * width /1000000)%>%
   filter(!is.na(volume))%>%
   select(price, name, category,volume)%>%
   mutate(price = log(price))
```


```{r}
set.seed(123)
ikea_split <- initial_split(ikea_df, strata = price)
ikea_train <- training(ikea_split)
ikea_test <- testing(ikea_split)

set.seed(234)
ikea_folds <- bootstraps(ikea_train, strata = price)
ikea_folds
```


With **usemodels** We can capture the non-parametrics trends

```{r}
use_ranger(price ~ ., data = ikea_train)
```

```{r}

ranger_recipe <-
  recipe(formula = price ~ ., data = ikea_train) %>%
  step_other(name, category, threshold = 0.01) %>%
  step_clean_levels(name, category) 

ranger_spec <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_mode("regression") %>% 
  set_engine("ranger")

ranger_workflow <- 
  workflow() %>% 
  add_recipe(ranger_recipe) %>% 
  add_model(ranger_spec) 

set.seed(9876)
doParallel::registerDoParallel()
ranger_tune <-
  tune_grid(ranger_workflow,
    resamples = ikea_folds,
    grid = 11
  )

```



```{r}
show_best(ranger_tune, metric = "rmse")
```

```{r}
autoplot(ranger_tune)
```
```{r}
select_best(ranger_tune)
final_rf <- ranger_workflow %>%
  finalize_workflow(select_best(ranger_tune))
ikea_fit <- last_fit(final_rf, ikea_split)
collect_metrics(ikea_fit)

```

```{r}
collect_predictions(ikea_fit) %>%
  ggplot(aes(price, .pred)) +
  geom_abline(lty = 2, color = "red") +
  geom_point(alpha = 0.5, color = "gray") +
  coord_fixed()+
  labs(title = 'Adj for random Forest {Price predictions}',
       x='Price',
       y = 'Price Predictions')
```

With the random forest we have a good model, but, maybe with Neuronal Network for this prediction  improve  the output


```{r}
library(keras)
library(tfdatasets)

ikea_keras <- ikea%>%
   select(where(is.numeric),-item_id)%>%
  na.omit()
   
   
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}


ikea_keras_n<-as.data.frame(lapply(ikea_keras, normalize))
#ikea_keras_n$price <- ikea_keras$price
set.seed(123)

ikea_split <- initial_split(ikea_keras_n, strata = price)
ikea_train <- training(ikea_split)%>%na.omit()
ikea_test <- testing(ikea_split)%>%na.omit()


```

```{r}
model %>% 
  layer_dense(units = 15, activation = 'relu',input_shape = c(3) ) %>% 
  layer_dense(units = 8, activation = 'relu') %>%
  layer_dense(units = 1, activation = 'linear')

model %>% compile(
  loss = 'mse',
  optimizer = optimizer_rmsprop(),
  metrics = list("mean_absolute_error")
)

history <- model %>% fit(
  x = ikea_train%>%
    select(-c(price))%>%
    as.matrix(), 
  y = ikea_train%>%
    select(price)%>%
    as.matrix(), 
  validation_split=0.2,
  epochs = 50, batch_size =2
)
```
```{r}
plot(history)
```

```{r}
library(MLmetrics)
model%>%
  evaluate(ikea_test%>%select(-c(price))%>%as.matrix(),ikea_test%>%select(price)%>%as.matrix())
```


## Last Alternative

```{r}
set.seed(123)
ikea_split <- initial_split(ikea_df%>%
                              select(-c(name,category)), strata = price)%>%na.omit()
ikea_train <- training(ikea_split)
ikea_test <- testing(ikea_split)

set.seed(234)
ikea_folds <- bootstraps(ikea_train, strata = price)
ikea_folds
use_xgboost(price~.,data = ikea_train)
```
```{r}
xgboost_recipe <- 
  recipe(formula = price ~ ., data = ikea_train) %>% 
  step_zv(all_predictors()) 

xgboost_spec <- 
  boost_tree(trees = tune(), min_n = tune(), tree_depth = tune(), learn_rate = tune(), 
    loss_reduction = tune(), sample_size = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("xgboost") 

xgboost_workflow <- 
  workflow() %>% 
  add_recipe(xgboost_recipe) %>% 
  add_model(xgboost_spec) 



set.seed(77)
doParallel::registerDoParallel()
xgboost_tune <-
  tune_grid(xgboost_workflow, 
            resamples =  ikea_folds, 
            grid =10)

xgboost_tune
show_best(xgboost_tune, metric = "rmse")
```


```{r}
autoplot(xgboost_tune)
```


```{r}
select_best(xgboost_tune)
```

```{r}
final_xgb <- xgboost_workflow %>%
  finalize_workflow(select_best(xgboost_tune))

ikea_fit <- last_fit(final_xgb, ikea_split)
collect_metrics(ikea_fit)
```

With this model , We dont cant working! 
